---
title: "RSelenium workshop useR2018! Brisbane"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

These are my notes from the *Ultimate online collection toolbox: Combining RSelenium and Rvest* workshop at useR2018! Brisbane for the second part of the workshop using Docker and RSelenium. 

[user2018! Workshop notes](https://gist.github.com/HanjoStudy/aeb331b7a277be9639f3cfb3bf875ba2)

I also found his RSelenium [vignette](http://rpubs.com/johndharrison/RSelenium-Basics) as a good reference.

```{r}
# We will be using `devtools` to install the necessary dependencies from `github`

# devtools::install_github("johndharrison/binman")
# devtools::install_github("johndharrison/wdman")
# devtools::install_github("ropensci/RSelenium")

# Once you have installed all the packages, remember to load `RSelenium` into your workspace

library(RSelenium)
library(rvest)
library(tidyverse)
```

#  Using Docker

RSelenium is notorious for instability and compatibility issues. It is thus amazing that they now have a docker image for headless webdrivers. Running a docker container standardises the build across OS's and removes many of the issues user may have relating to JAVA/browser version/selenium version


After installing Docker toolbox and open quickstart terminal. Take note of the IP address.

Docker is configured to use the default machine with IP 192.168.99.100.

Now open dockerhub.com and go to selenium nodes to get a **dockerfile**
https://hub.docker.com/u/selenium/ which is the source code of an image.

Build the **dockerfile** to create the image of the container. The image is just the "compiled version" of the ["source code" which is the Dockerfile](http://blog.manageacloud.com/entry/dockerising-puppet).

Once you have the image of the container, you should redistribute it using the registry. The registry is like a git repository -- you can push and pull images.

We will use standalone-chrome-debug/ and copy the pull command into the terminal, use latest **image**. 

Next, you can use the **image** to run containers. A running container is very similar, in many aspects, to a virtual machine (but without the hypervisor).
 
 https://stackoverflow.com/questions/23735149/what-is-the-difference-between-a-docker-image-and-a-container
> To use a programming metaphor, if an image is a class, then a container is an instance of a class-a runtime object.

Local images can be listed by running docker images in the terminal.

Important Docker commands to remember include run, stop and rm.

# Starting your Selenium Server 

docker run --name chrome  -v /dev/shm:/dev/shm -d -p 4445:4444 -p 5901:5900 selenium/standalone-chrome-debug:latest

* `-name` name your container, otherwise docker will with a funny name ;-)
* `-v` mount volume
* `-d` detached mode to be a background process
* `-p` port mapping (external:internal) open ports in debug mode
 `selenium/standalone-chrome-debug:latest



# Attach your viewport (TightVNC & Vinagre)

We can use Virtual Network Computing (VNC) viewers to view what is happening

add the IP and port with 192.168.99.100::5901 password is secret as per the standalone-chrome-debug documentation

```{r}
# Open and navigate

# This command sets up a list of the parameters we are going to send to selenium to kick off
remDr <- remoteDriver(remoteServerAddr = "192.168.99.100",
                      port = 4445L, 
                      browser = "chrome")

# Notice the strange notation? Thats because of Java object.method
remDr$open()
```


Finally - RSelenium is operational, check in the VNC
 * Quick overview of the tools you will be using
 * Useful functions written in javascript that I find useful
 * Obsure and fun functions
 * Combine it all into a case study.
 

```{r}
# Use method navigate to drive your browser around
remDr$navigate
remDr$navigate("http://www.google.com")
remDr$navigate("http://www.bing.com")
# Use methods back and forward to jump between pages
remDr$goBack()
remDr$goForward()
```
 
# Using keys and Scrolling
 
```{r}
# We can send various keys to the Selenium
RSelenium:::selKeys %>% names()

# Note the notation of the command object$method(list = "command)
remDr$sendKeysToActiveElement(list(key = "page_down"))
remDr$sendKeysToActiveElement(list(key = "page_up"))

# We also send Javascript to the page - this becomes important if you want to know how far down you have scrolled...
remDr$executeScript("return window.scrollY", args = list(1))
remDr$executeScript("return document.body.scrollHeight", args = list(1))

remDr$executeScript("return window.innerHeight", args = list(1))
remDr$executeScript("return window.innerWidth", args = list(1))

remDr$sendKeysToActiveElement(list(key = "home"))
remDr$sendKeysToActiveElement(list(key = "end"))
```
 
# Interacting with the DOM

```{r}
# The DOM stands for the Document Object Model. It is a cross-platform and language-independent convention for representing and interacting with objects in HTML, XHTML and XML documents. To get the whole DOM:
  
gethtml <- function(remDr){
remDr$getPageSource() %>% 
    .[[1]] %>% 
    read_html()
}
remDr %>% gethtml(.) 

# To interact with the DOM, we will use the `findElement` method:
  
#  Search by id, class, selector, xpath

remDr$navigate("http://www.google.com/")

# This is equivalent to html_nodes
webElem <- remDr$findElement(using = 'class', "gsfi")

webElem$highlightElement()
 
# Having identified the element we want to interact with, we have a couple of methods that we can apply to the object:

webElem$clickElement()
webElem$click(2)

# Cannot interact with objects not on screen. Can only click on objects in view
remDr$mouseMoveToLocation(webElement = webElem)

webElem$sendKeysToActiveElement(list(key = 'down_arrow', key = 'down_arrow', key = 'enter'))
webElem$sendKeysToActiveElement(list("Hallo World", key = 'enter'))
```
# Nice to have functions

```{r}
remDr$maxWindowSize()
remDr$getTitle()
remDr$screenshot(display = TRUE)

b64out<- remDr$screenshot()
writeBin(RCurl::base64Decode(b64out, "raw"), 'screenshot.png')

# Scroll into view
remDr$executeScript("arguments[0].scrollIntoView(true);", args = list(webElem))

# Building a RSelenium pipe function

# RSelenium has 2 types of commands:
#   
# * Those with side-effects (action)
# * Those that returns information we want to push into `rvest`
# 
# For the 1st case, we would want to return the driver object as the state of it has changed

navi <- function(remDr, site = "www.google.com"){
  remDr$navigate(site)
  return(remDr)
}

remDr %>% navi(., "www.google.com")
```


# Case Study: A Tour of the winelands!


Australia is famous for its wines! Lets find out a little bit more about the wine region 
 * Go to vivino.com
 * Collect 2 pages worth of information
  Name of wine farm, name of wine, star rating, count of ratings
 
```{r go to website}
# Navigate to vivino website
remDr$navigate("https://www.vivino.com/")
# Check the url
remDr$getCurrentUrl()

# Let's use our gethtml function to get the DOM
vinohtml <- remDr %>% gethtml(.)
# Check the class
class(vinohtml)

# Next isolate the button we need to click on to explore wines. We could find the name from right click and inspect to find CSS selector
webElem <- remDr$findElement("css", '.explore-widget__main__submit__button')
webElem$getElementAttribute("class")
webElem$getElementAttribute("id")
# Highlight and click button
webElem$highlightElement()
webElem$clickElement()
# Now we are in the next page wee can create a scroll to and highlight function
scrollTo <- function(remDr, webElem){
  remDr$executeScript("arguments[0].scrollIntoView(true);", args = list(webElem))
  webElem$highlightElement()
}
# I use xpath here, just because I want to illustrates the handy function: starts with
# I am trying to isolate where I can fill in the name of the country I am looking to search
webElem <- remDr$findElements("xpath", '//input[starts-with(@class, "filterPills")]')

scrollTo(remDr, webElem[[2]])

webElem[[2]]$clickElement()
webElem[[2]]$sendKeysToActiveElement(list("Australia"))

webElem <- remDr$findElements("css", '.pill__inner--7gfKn')

# How I identify the correct webelem to click on
country_elem <- webElem %>% 
  sapply(., function(x) x$getElementText()) %>% 
  reduce(c) %>% 
  grepl("Australia", .) %>% 
  which

scrollTo(remDr, webElem[[country_elem]])

webElem[[country_elem]]$clickElement()

# Some pages need you to scroll to the bottom in order for more content to load. Vivino is one of them

remDr$executeScript("return window.scrollY", args = list(1))
remDr$executeScript("return document.body.scrollHeight", args = list(1))

remDr$sendKeysToActiveElement(list(key = "end"))
remDr$executeScript("return window.scrollY", args = list(1))

# Now we done with RSelenium, on to rvest! We will read the this page to and XML document

pg <- remDr$getPageSource() %>% .[[1]] %>% 
  read_html()
# We will collect specific info frfom this page using the CSS selector nodes and create a function collect_info
collect_info <- function(pg){
  farm <- pg %>% html_nodes(".vintageTitle__winery--2YoIr") %>% 
    html_text()
  
  wine <- pg %>% html_nodes(".vintageTitle__wine--U7t9G") %>% 
    html_text()
  
  rating <- pg %>% html_nodes("span.vivinoRating__rating--4Oti3") %>% 
    html_text() %>% 
    as.numeric
  
  rating_count <- pg %>% html_nodes("span.vivinoRating__ratingCount--NmiVg") %>% 
    html_text() %>% 
    gsub("[^0-9]", "",.) %>% 
    as.numeric
  
  data.frame(farm, wine, rating, rating_count)
}

collect_info(pg)


```

